Computational Six-bar Synthesis for Implementing Dynamic Behavior

### 2019-01-26 draft.tex
Modified for Ron's comments, abstract and conclusion added

\author{Mark~M.~Plecnik %,~\IEEEmembership{Member,~IEEE,}
        and~Ronald~S.~Fearing,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{M.~Plecnik is a postdoctoral scholar in the Biomimetic Millisystems Lab at the University of California, Berkeley, CA, 94720 USA e-mail: {\tt\small mplecnik@berkeley.edu}}% <-this % stops a space
\thanks{R.~S.~Fearing is director of the Biomimetic Millisystems Lab and a professor in the Department of Electrical Engineering \& Computer Science, University of California, Berkeley, CA, 94720 USA e-mail: {\tt\small ronf@eecs.berkeley.edu}}% <-this % stops a space
\thanks{Manuscript received November xx, 2018; revised Month xx, 20xx.}}

@@

\begin{abstract}
The abstract goes here.
\end{abstract}

\begin{IEEEkeywords}
IEEE, IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

@@

\section{Introduction}
\label{sec:intro}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{here} are no simple tools for designing dynamic machines.
The leading approaches are based in optimization and intuition.
We demonstrate a method that excludes the former and lessens dependence on the latter.
This work is enabled by a new algorithm in numerical homotopy continuation that can find nearly complete solution sets of highly nonlinear systems of equations.
%
The connection to design occurs as these systems of equations comprise of geometric design constraints, and their variables are design parameters.
Rather than search through the design space for a set of parameters that satisfy all constraints and minimize some objective, design constraints are posed as systems with isolated roots, where gathering roots is equivalent to compiling candidate design parameters.  The result is a thorough exploration of the design space.

@@

Another dynamic consideration is the presence of vibrations in high speed machinery.  
Matthew and Tesar \cite{matthewCamSystemDesign1976} considered the effects of vibrations and inertial forces on cam design.
Li and Kota \cite{liDynamicAnalysisCompliant2002} analyzed the frequency response of a micro machined stroke amplifying mechanism for an electrostatic actuator and conducted sensitivity analyses useful for synthesis.
Motivated by their investigation of parallel manipulators, Martini et al. \cite{martiniElastodynamicBehaviorBalanced2014} study mass balanced and elastically compensated closed chains through the addition of weights and springs.
Design methods that consider the kineto-elastodynamic effects in mechanisms were presented by Imam and Sandor \cite{imamHighSpeedMechanismDesign1975}.
Tantanawat and Kota \cite{tantanawatDesignCompliantMechanisms2007} investigated the benefits of strain energy storage in the dynamic performance of a compliant flapping mechanism.

@@

One motivation for this work is to design dynamic machines suitable for legged robots.
The literature indicates various design principles and outstanding challenges to direct the formulation of design requirements.
With respect to small hexapedal running robots, Clark et al. \cite{clarkBiomimeticDesignFabrication2001} and Hoover et al. \cite{hooverBioinspiredDesignDynamic2010} indicate the importance of passive mechanics, self-stabilization, open-loop/feedforward control, minimal actuation, and integrated manufacturing techniques in order to negotiate the strict limits on power, computation, and weight associated with of small robots.
Zarrouk et al. \cite{zarroukDynamicLeggedLocomotion2015} addressed the need of high speed turning in a hexapedal runner by taking advantage of dynamic roll and pitch instabilities.
The challenges of legged robots listed by Buehler \cite{buehlerDynamicLocomotionOne2002} include underactuated dynamics, friction limited horizontal ground forces, short stance times to apply control, bandwidth limitations, and limited power/energy densities of commercial actuators.
Collins et al. \cite{collinsEfficientBipedalRobots2005} leveraged passive-dynamics to create robots that mimic human walking with simple actuators that do not require precise joint-angle control.
Curran et al. \cite{curranDesignSeriesElasticActuators2008} indicated the role of series-elastic actuation in decoupling the limits of a DC motor from a dynamic task.
Semini et al. \cite{seminiDesignHyQHydraulically2011} stress the importance of high powered actuators.
In the analysis of a symmetric five-bar linkage, Kenneally and Koditschek \cite{kenneallyLegDesignEnergy2015} measured performance according to the conversion of battery energy into body energy, the minimization of touchdown losses, and the storing/return of energy during stance.
Blackman et al. \cite{blackmanLegDesignRunning2017} extended their analysis, highlighting the ability of this symmetric five-bar to achieve greater speeds and stability in one configuration, but greater jump height in another.
Brown et al. \cite{brownDesignMethodologyLinkage2017} analyzed the ability of this five-bar and other linkage designs to balance workloads between motors.
Kalouche \cite{kaloucheGOATLeggedRobot2017} designed a spatial linkage based on this five-bar.
Wensing et al. \cite{wensingProprioceptiveActuatorDesign2017} demonstrated the importance of torque density, high-bandwidth force control, and impact mitigation in quadrupedal running robots.

@@

@@

\begin{figure}[!t]
\centering
\includegraphics[width=1\linewidth]{dynamic_model}
\caption{A mock-up dynamic system used to inform desirable kinematic properties of a to-be-designed linkage.  The fixed motor is connected in series with a spring to an input crank.  Without any linkage existing yet, a user defined angle-arclength relationship describes how torques at the crank transform to forces at the masses.}
\label{dynamic_model}
\end{figure}

@@

For example, the red points shown in Fig. \ref{clickspec_path} were clicked with a mouse.  The interpolated curve is parameterized by the Fourier series,
%\begin{equation}
%\begin{tabular}{cr}
%\multirow{3}[0]{*}{$\mathcal{C} = \begin{Bmatrix} \tilde{x}(t) \\ \tilde{y}(t) \end{Bmatrix}, \hspace{2mm} $}
%& $\tilde{x}(t) = \frac{1}{2}a_0 + \textstyle\sum\limits_{k=1}^{o}(a_k\cos 2\pi kt + b_k\sin 2\pi kt)$ \\
%& \vspace{-2mm} \\
%& $\tilde{y}(t) = \frac{1}{2}a_0 + \textstyle\sum\limits_{k=1}^{o}(a_k\cos kt + b_k\sin kt)$ \\
%\end{tabular}
%\end{equation}
\begin{align}
&\tilde{x}(\tau) = \tfrac{1}{2}a_0 + \textstyle\sum\limits_{k=1}^{o}\!\Big( a_k\cos (2\pi k\tau) + b_k\sin (2\pi k\tau) \Big) \nonumber\\[5pt]
&\tilde{y}(\tau) = \tfrac{1}{2}c_0 + \textstyle\sum\limits_{k=1}^{o}\!\Big( c_k\cos (2\pi k\tau) + d_k\sin (2\pi k\tau) \Big)
\label{fourier_interp_path}
\end{align}
%such that $\mathcal{C} = \{ (u,v) \;|\; u = \tilde{x}(t),\; v = \tilde{y}(t) \;\forall\; t \in [0,1] \}$
such that $\mathcal{C} = \left\lbrace \left( \tilde{x}(t), \tilde{y}(t) \right) |\; \tau \in [0,1] \right\rbrace$.
The values of Fourier coefficients for the example problem are displayed in Appendix \ref{app:fourier_coefficients}.
Order $o$ may be freely specified.

@@

We follow a similar process for specifying mechanical advantage with a few modifications.
First, mechanical advantage $\gamma$ is defined as a function of normalized arclength $\hat{s}$ so that points are clicked with a mouse in the $\hat{s}$-$\gamma$ plane shown in Fig. \ref{clickspec_ma}.
Second, the endpoints at $\hat{s}\!=\!0$ and $\hat{s}\!=\!1$ are always specified and share the same $\gamma$ value.
And third, after interpolation the resulting Fourier series $\gamma(\hat{s})$ must be vertically shifted.
For a fully rotatable input crank, the area under $\gamma(\hat{s})$ must be $2\pi$.
To see this, note that mechanical advantage is equal to the ratio of input and output velocities,
\begin{equation}
\frac{d\phi}{d\hat{s}} = \gamma(\hat{s}).
\end{equation}
For a full traversal of $\mathcal{C}$, the crank must rotate $2\pi$, or rather
\begin{equation}
2\pi = \int_{0}^{1} \gamma(\hat{s}) d\hat{s}.
\end{equation}
Next, function $\gamma(\hat{s})$ is rewritten to accept a non-normalized arclength $s$ argument,
\begin{equation}
\gamma(s) := \frac{\gamma(s/s_\text{total})}{s_\text{total}}
\label{gamma_of_s}
\end{equation}
Note we take a notational liberty in Eqn. (\ref{gamma_of_s}) by redefining function $\gamma$ in terms of itself instead of making up new notation.
Integration of $\gamma(s)$ yields an angle-arclength relationship which creates the specified mechanical advantage,
\begin{equation}
\phi(s) = \int_{0}^{s_\text{total}} \gamma(s)ds + \text{constant}.
\end{equation}
For our example, this curve is plotted in Fig. \ref{clickspec_angle}.  For convenience, the constant of integration is chosen so that $\phi(0) = 0$.

@@

And finally, the forces acting on masses $m$ and $M$ follow the diagrams drawn in Fig. \ref{dynamic_model_detail}.
That is,
\begin{align}
&F_t\cos\nu - F_n\sin\nu - F_b = m\ddot{x}, \nonumber\\
&F_t\sin\nu + F_n\cos\nu = m\ddot{y}, \nonumber\\
&F_b = M\ddot{X},
\end{align}
and if $m$ and $M$ are in contact,
\begin{equation}
\ddot{x} = \ddot{X}
\end{equation}
else
\begin{equation}
F_b = 0.
\end{equation}
$F_n$ is the constraint force normal to $\mathcal{C}$, $F_b$ is the reaction force between $m$ and $M$, $(x,y)$ are the coordinates of $m$ constrained to $\mathcal{C}$ according to Eqn. (\ref{fourier_interp_path_arc}), $X$ is the coordinate of $M$, and $\psi$ is the tangency angle of $\mathcal{C}$ at $(x,y)$, that is
\begin{equation}
\nu = \arctan\frac{\dot{y}}{\dot{x}}.
\label{tangency_angle}
\end{equation}
Eqns. (\ref{torque-speed})--(\ref{tangency_angle}) in conjunction with $x(s)$, $y(s)$, $\gamma(s)$, and $\phi(s)$ specified in Section \ref{sec:spec_mech_char} form the equations of motion.  To solve these equations, they were rewritten into the form of an initial value problem for use with standard ODE solvers.

@@

After determining desired mechanism characteristics in Section \ref{sec:dynamic_mock-up}, our objective is to synthesize a linkage that exhibits those characteristics.
In particular, we desire a physical instantiation of $x(s)$, $y(s)$, and $\phi(s)$.
The latter of the three is desired more so for its derivative, $\gamma(s)$, rather than itself, but we employ it directly as a design goal nonetheless.
The design problem of finding a linkage that creates a desired endpoint path is called \emph{path generation}.
When this path is additionally coordinated with the angle of an input crank, this problem is sometimes called \emph{timed curve generation} \cite{dijksmanMotionGeometryMechanisms1976}.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=1\linewidth]{synthesis_diagram}
\caption{Diagram describing the notation used in the synthesis formulation.  Linkage pivots in a reference configuration are marked with complex numbers $A$, $B$, $C$, $D$, $F$, $G$, and $H$.  The $j^\text{th}$ displaced configuration is shown here.}
\label{synthesis_diagram}
\end{figure}

@@

To begin deriving the synthesis equations, first form three independent vector loop equations from Fig. \ref{clickspec},
\medmuskip=2mu
\begin{align}
&R_j(H-C) = P_j - A - Q_j(C-A) - U_j(P_0-H) \label{loopR1}\\
&S_j(F-B) = P_j - B - U_j(P_0-F) \label{loopS1}\\
&T_j(G-D) = A-B + Q_j(C-A) + R_j(G-C) - S_j(D-B) \label{loopT1}\\
&\hspace{50mm} j=1,\ldots,N-1 \nonumber
\end{align}
\medmuskip=4mu

@@

Start systems are commonly constructed as products of linear expressions in order to easily obtain all their roots.
By picking one linear expression from each equation, then solving the resulting square linear system, a startpoint is found.  
Doing this for all valid combinations of linear expressions finds all startpoints.
The problem arises that a start system constructed this way tends to comprise of many more monomials than the target system, which tends to have a sparse structure for the problems of interest.
This usually means there will be drastically more finite startpoints than endpoints, with the far majority of homotopy paths tracking toward roots at infinity.

FRG solves this problem by constructing start systems with the exact monomial structure as the target system.
This is accomplished by generating a random linkage and extracting a start system from its motion and a startpoint from its dimensions.
This single startpoint will indeed track to a finite root of the target system.
To get a second root, this process is repeated.
As the finite target root set we aim to obtain is very large, chances are that this second startpoint will track to a different endpoint, with no guarantee.
Repeating this process, roots are accumulated.
As FRG trials progress, eventually the odds of acquiring a new root become unfavorable.
More and more duplicate roots are computed.
FRG trades away infinite root computations for duplicate root computations.  
For sparse systems, the latter tends to be far fewer than the former, making it a good trade.
The frequency of duplicate roots was characterized in \cite{plecnikStudyFindingFinite2017}.
Tracking their occurrence allows an in-process estimate of the percentage of the total root set that has been obtained.

FRG mediates additional computation savings by exploiting known solution structures in a straightforward way.
For linkage synthesis equations, this structure is primarily provided by the presence of linkage cognates.
The cognate of a single degree-of-freedom linkage is another linkage with different dimensions that exactly reproduces some aspect of the original linkage's continuous motion.
For a given linkage type (e.g. Stephenson II) and motion of interest (e.g. timed curve generation), the presence and number of cognates is often known.
As well, geometric transformations between cognates are known too.
Using these transformations, an entire set of cognate roots can be quickly computed from one endpoint.
Each root in a cognate set is a separate isolated solution, and cognate sets have no intersection with each other.
Combining cognate structures with other existing symmetries (if present) partitions target roots into a smaller number of sets, thereby reducing the expected computational load by the multiple of the size of a single solution set.

@@

Although physically relevant values were not used, the rest of the variables and parameters within $\mathbf{z}$ and $\mathbf{q}$ are computed from the forward kinematics equations of a physical six-bar model.
Physical or not, the result still satisfies Eqn. (\ref{system}), which is our goal at the moment.
These forward kinematics equations are included in Appendix \ref{app:fwd_kin}.
As a six-bar is a one degree-of-freedom linkage, in order to extract random configurations from its motion, we must provide random values for a single configuration parameter.
We choose $R_j\*U_j$, $j=1,\ldots,7$, the complex number associated with angle $\rho_j-\mu_j$, because it makes the forward kinematics computations simple and fast.
It may be noted that the complexity of the solution process of the forward kinematics is dependent on the choice of a specified configuration parameter.
Perhaps intuitively, $R\*U$ is a good choice because it defines one angle of the floating four-bar $DGHF$, which segments calculations to one variable at a time after that.
Solving the forward kinematics equations provides all remaining values in $\mathbf{z}$ and $\mathbf{q}$.
A homotopy path may then be tracked from the startpoint $\mathbf{z}$ that solves the system defined by $\mathbf{q}$ to a finite root that solves our target system, Eqn. (\ref{system}).

@@

Using the start system construction method of Section \ref{sec:start_sys} and exploiting the cognate structure of Section \ref{sec:cognates}, FRG was applied to find the ab initio roots $\mathbf{z}$ of a numerically general target system $\mathcal{S}(\mathbf{z},\mathbf{q}_1)=0$.
Target parameters $\mathbf{q}_1$ were randomly generated and are printed in Appendix \ref{app:fpm}.
After generating this ab initio solution, these roots were used repeatedly in conjunction  with the parameter homotopy method to solve for any other system $\mathcal{S}(\mathbf{z},\mathbf{q}_2)=0$, where $\mathbf{q}_2$ might be defined by a specific synthesis task.
In Section \ref{sec:leg_app}, we will define $\mathbf{q}_2$ according to analyses in Section \ref{sec:dynamic_mock-up}, to design a novel machine.

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.6]{frg_results}
\caption{The accumulation of roots over the procession of the FRG algorithgm.  An estimated 99.0\% of roots were found in $3.56 \times 10^6$ trials.  To find 99.9\% would take about 50\% more computational effort.}
\label{frg_results}
\end{figure}

@@

@@

Fourier coefficients for example's path

>>>>

\title{Large Scale Root Finding for the Kinematic Design of Mechanisms with Desired Dynamic Behavior}

\author{Mark~M.~Plecnik %,~\IEEEmembership{Member,~IEEE,}
        and~Ronald~S.~Fearing,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{M.~Plecnik is an assistant professor in the Department of Aerospace and Mechanical Engineering at the University of Notre Dame, IN, 46556 USA e-mail: {\tt\small plecnikmark@nd.edu}}% <-this % stops a space
\thanks{R.~S.~Fearing is director of the Biomimetic Millisystems Lab and a professor in the Department of Electrical Engineering \& Computer Science, University of California, Berkeley, CA, 94720 USA e-mail: {\tt\small ronf@eecs.berkeley.edu}}% <-this % stops a space
\thanks{Manuscript received January xx, 2019; revised Month xx, 2019.}}

@@

\begin{abstract}
Designing a robotic mechanism to perform some desired dynamic behavior under limited actuation power is a challenge.
Descriptions of dynamic requirements inherently exist in the time domain while extant mechanism synthesis techniques are predominantly geometric in nature.
To bridge this gap, we consider the dynamics of a simplified ``mock-up'' model of a motor acting through a spring and mechanism to push an inertia.
This model excludes the mechanism's dimensions and topology in place of user-defined mechanism characteristics.
The characteristics that produce desired dynamic behavior serve as a goal for a to-be-designed mechanism discovered during subsequent kinematic synthesis.
Following this, the synthesis method employed must be capable of sufficiently matching user-defined nonlinearities.
Linkages of the six-bar topology provide this capability but are challenged with design equations of very high degree that have not been solved before.
In this work, we solve one such system of design equations using the Finite Root Generation technique.
Our approach is motivated by an application for small legged robots to increase power density through kinematic design rather than actuator sizing.
While not possible for a directly driven mechanism, we show how this is done using series-elastic actuation.
We design leg mechanisms capable of continuously recycling a foot path while producing locomotive power within a single stride beyond its actuator's limit.
Candidate designs are presented that are capable of producing 3.0 times the actuator's power in simulation.
Experimental results of one such mechanism demonstrated a decrease from the ideal down to 2.6 times the actuator's power.
\end{abstract}

\begin{IEEEkeywords}
Mechanism dynamics, kinematic synthesis, robot design
\end{IEEEkeywords}

@@

\section{Introduction}
\label{sec:intro}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{here} are no simple tools for designing dynamic machines.
The leading approaches are based in optimization and intuition.
We demonstrate a method that excludes the former and lessens dependence on the latter.
This work is enabled by a new algorithm in numerical homotopy continuation that can find nearly complete solution sets of highly nonlinear systems of equations.
%
The connection to design occurs as these systems of equations comprise geometric design constraints, and their variables are design parameters.
Rather than search through the design space for a set of parameters that satisfy all constraints and minimize some objective, design constraints are posed as systems with isolated roots, where gathering roots is equivalent to compiling candidate design parameters.  The result is a thorough exploration of the design space.

@@

Another dynamic consideration is the presence of vibrations in high speed machinery.  
Matthew and Tesar \cite{matthewCamSystemDesign1976} considered the effects of vibrations and inertial forces on cam design.
Li and Kota \cite{liDynamicAnalysisCompliant2002} analyzed the frequency response of a micro machined stroke amplifying mechanism for an electrostatic actuator and conducted sensitivity analyses useful for synthesis.
Motivated by their investigation of parallel manipulators, Martini et al. \cite{martiniElastodynamicBehaviorBalanced2014} studied mass balanced and elastically compensated closed chains through the addition of weights and springs.
Design methods that consider the kineto-elastodynamic effects in mechanisms were presented by Imam and Sandor \cite{imamHighSpeedMechanismDesign1975}.
Several authors have investigated improving compliant wing flapping mechanisms through careful design.
Baek et al. \cite{baekEfficientResonantDrive2009} consider the use of resonance to reduce battery consumption, Khatait et al. \cite{khataitCompliantDesignFlapping2006} minimized peak driving torque, and Tantanawat \& Kota \cite{tantanawatDesignCompliantMechanisms2007} investigated the benefits of dynamic strain energy storage.

@@

One motivation for this work is to design dynamic machines suitable for legged robots.
The literature indicates various design principles and outstanding challenges to direct the formulation of design requirements.
With respect to small hexapedal running robots, Clark et al. \cite{clarkBiomimeticDesignFabrication2001} and Hoover et al. \cite{hooverBioinspiredDesignDynamic2010} indicate the importance of passive mechanics, self-stabilization, open-loop/feedforward control, minimal actuation, and integrated manufacturing techniques in order to negotiate the strict limits on power, computation, and weight associated with of small robots.
Zarrouk et al. \cite{zarroukDynamicLeggedLocomotion2015} addressed the need of high speed turning in a hexapedal runner by taking advantage of dynamic roll and pitch instabilities.
The challenges of legged robots listed by Buehler \cite{buehlerDynamicLocomotionOne2002} include underactuated dynamics, friction limited horizontal ground forces, short stance times to apply control, bandwidth limitations, and limited power/energy densities of commercial actuators.
Collins et al. \cite{collinsEfficientBipedalRobots2005} leveraged passive-dynamics to create robots that mimic human walking with simple actuators that do not require precise joint-angle control.
Curran et al. \cite{curranDesignSeriesElasticActuators2008} indicated the role of series-elastic actuation in decoupling the limits of a DC motor from a dynamic task.
Semini et al. \cite{seminiDesignHyQHydraulically2011} stressed the importance of high powered actuators.
In the analysis of a symmetric five-bar linkage, Kenneally and Koditschek \cite{kenneallyLegDesignEnergy2015} measured performance according to the conversion of battery energy into body energy, the minimization of touchdown losses, and the storing/return of energy during stance.
Blackman et al. \cite{blackmanLegDesignRunning2017} extended their analysis, highlighting the ability of this symmetric five-bar to achieve greater speeds and stability in one configuration, but greater jump height in another.
Brown et al. \cite{brownDesignMethodologyLinkage2017} analyzed the ability of this five-bar and other linkage designs to balance workloads between motors.
Kalouche \cite{kaloucheGOATLeggedRobot2017} designed a spatial linkage based on this five-bar.
Wensing et al. \cite{wensingProprioceptiveActuatorDesign2017} demonstrated the importance of torque density, high-bandwidth force control, and impact mitigation in a quadrupedal running robot.

@@

\begin{figure}[!b]
\centering
\includegraphics[width=1\linewidth]{dynamic_model}
\caption{A mock-up dynamic system used to inform desirable kinematic properties of a to-be-designed linkage.  The fixed motor is connected in series with a spring to an input crank.  Without any linkage existing yet, a user defined angle-arclength relationship describes how torques at the crank transform to forces at the masses.}
\label{dynamic_model}
\end{figure}

@@

@@

For example, the red points shown in Fig. \ref{clickspec_path} were entered manually with a computer mouse.  The interpolated curve is parameterized by the Fourier series,
%\begin{equation}
%\begin{tabular}{cr}
%\multirow{3}[0]{*}{$\mathcal{C} = \begin{Bmatrix} \tilde{x}(t) \\ \tilde{y}(t) \end{Bmatrix}, \hspace{2mm} $}
%& $\tilde{x}(t) = \frac{1}{2}a_0 + \textstyle\sum\limits_{k=1}^{o}(a_k\cos 2\pi kt + b_k\sin 2\pi kt)$ \\
%& \vspace{-2mm} \\
%& $\tilde{y}(t) = \frac{1}{2}a_0 + \textstyle\sum\limits_{k=1}^{o}(a_k\cos kt + b_k\sin kt)$ \\
%\end{tabular}
%\end{equation}
\begin{align}
&\tilde{x}(\tau) = \tfrac{1}{2}a_0 + \textstyle\sum\limits_{k=1}^{o}\!\Big( a_k\cos (2\pi k\tau) + b_k\sin (2\pi k\tau) \Big) \nonumber\\[5pt]
&\tilde{y}(\tau) = \tfrac{1}{2}c_0 + \textstyle\sum\limits_{k=1}^{o}\!\Big( c_k\cos (2\pi k\tau) + d_k\sin (2\pi k\tau) \Big)
\label{fourier_interp_path}
\end{align}
%such that $\mathcal{C} = \{ (u,v) \;|\; u = \tilde{x}(t),\; v = \tilde{y}(t) \;\forall\; t \in [0,1] \}$
such that $\mathcal{C} = \left\lbrace \left( \tilde{x}(\tau), \tilde{y}(\tau) \right) |\; \tau \in [0,1] \right\rbrace$.
The values of Fourier coefficients for the example problem are displayed in Appendix \ref{app:fourier_coefficients}.
Order $o$ may be freely specified.

@@

We follow a similar process for specifying mechanical advantage with a few modifications.
First, mechanical advantage $\gamma$ is defined as a function of normalized arclength $\hat{s}$ so that points are entered manually with a mouse in the $\hat{s}$-$\gamma$ plane shown in Fig. \ref{clickspec_ma}.
Second, the endpoints at $\hat{s}\!=\!0$ and $\hat{s}\!=\!1$ are always specified and share the same $\gamma$ value.
And third, after interpolation the resulting Fourier series $\gamma(\hat{s})$ must be vertically shifted.
For a fully rotatable input crank, the area under $\gamma(\hat{s})$ must be $2\pi$.
To see this, note that mechanical advantage is equal to the ratio of input and output velocities,
\begin{equation}
\frac{d\phi}{d\hat{s}} = \gamma(\hat{s}).
\end{equation}
For a full traversal of $\mathcal{C}$, the crank must rotate $2\pi$, or rather
\begin{equation}
2\pi = \int_{0}^{1} \gamma(\hat{s}) d\hat{s}.
\end{equation}
The Fourier coefficients of $\gamma(\hat{s})$ are given in Appendix \ref{app:fourier_coefficients} as values $(\alpha_k, \beta_k)$.

Next, function $\gamma(\hat{s})$ is rewritten to accept a non-normalized arclength $s$ argument,
\begin{equation}
\gamma(s) := \frac{\gamma(s/s_\text{total})}{s_\text{total}}
\label{gamma_of_s}
\end{equation}
Note we take a notational liberty in Eqn. (\ref{gamma_of_s}) by redefining function $\gamma$ in terms of itself instead of making up new notation.
Integration of $\gamma(s)$ yields an angle-arclength relationship which creates the specified mechanical advantage,
\begin{equation}
\phi(s) = \int_{0}^{s_\text{total}} \gamma(s)ds + \text{constant}.
\end{equation}
For our example, this curve is plotted in Fig. \ref{clickspec_angle}.  For convenience, the constant of integration is chosen so that $\phi(0) = 0$.

@@

And finally, the forces acting on masses $m$ and $M$ follow the diagrams drawn in Fig. \ref{dynamic_model_detail}.
That is,
\begin{align}
&F_t\cos\nu - F_n\sin\nu - F_b = m\ddot{x}, \nonumber\\
&F_t\sin\nu + F_n\cos\nu = m\ddot{y}, \nonumber\\
&F_b = M\ddot{X},
\end{align}
and if $m$ and $M$ are in contact,
\begin{equation}
\ddot{x} = \ddot{X}
\end{equation}
else
\begin{equation}
F_b = 0.
\end{equation}
$F_n$ is the constraint force normal to $\mathcal{C}$, $F_b$ is the reaction force between $m$ and $M$, $(x,y)$ are the coordinates of $m$ constrained to $\mathcal{C}$ according to Eqn. (\ref{fourier_interp_path_arc}), $X$ is the coordinate of $M$, and $\nu$ is the tangency angle of $\mathcal{C}$ at $(x,y)$, that is
\begin{equation}
\nu = \arctan\frac{\dot{y}}{\dot{x}}.
\label{tangency_angle}
\end{equation}
Eqns. (\ref{torque-speed})--(\ref{tangency_angle}) in conjunction with $x(s)$, $y(s)$, $\gamma(s)$, and $\phi(s)$ specified in Section \ref{sec:spec_mech_char} form the equations of motion.  To solve these equations, they were rewritten into the form of an initial value problem for use with standard ODE solvers.

@@

After determining desired mechanism characteristics in Section \ref{sec:dynamic_mock-up}, our objective is to synthesize a linkage that exhibits those characteristics.
In particular, we desire a physical instantiation of $x(s)$, $y(s)$, and $\phi(s)$.
The latter of the three is desired more so for its derivative, $\gamma(s)$, rather than its direct curve, but we employ it directly as a design goal nonetheless.
The design problem of finding a linkage that creates a desired endpoint path is called \emph{path generation}.
When this path is additionally coordinated with the angle of an input crank, this problem is sometimes called \emph{timed curve generation} \cite{dijksmanMotionGeometryMechanisms1976}.

@@

\begin{figure}[!b]
\centering
\includegraphics[width=1\linewidth]{synthesis_diagram}
\caption{Diagram describing the notation used in the synthesis formulation.  Linkage pivots in a reference configuration are marked with complex numbers $A$, $B$, $C$, $D$, $F$, $G$, and $H$.  The $j^\text{th}$ displaced configuration is shown here.}
\label{synthesis_diagram}
\end{figure}

@@

To begin deriving the synthesis equations, first form three independent vector loop equations from Fig. \ref{synthesis_diagram},
\medmuskip=2mu
\begin{align}
&R_j(H-C) = P_j - A - Q_j(C-A) - U_j(P_0-H) \label{loopR1}\\
&S_j(F-B) = P_j - B - U_j(P_0-F) \label{loopS1}\\
&T_j(G-D) = A-B + Q_j(C-A) + R_j(G-C) - S_j(D-B) \label{loopT1}\\
&\hspace{50mm} j=1,\ldots,N-1 \nonumber
\end{align}
\medmuskip=4mu

@@

Start systems are commonly constructed as products of linear expressions in order to easily obtain all their roots.
By picking one linear expression from each equation, setting them equal to zero, then solving the resulting square linear system, a startpoint is found.  
Doing this for all valid combinations of linear expressions finds all startpoints.
The problem arises that a start system constructed this way tends to comprise many more monomials than the target system, which tends to have a sparse structure for the problems of interest.
This usually means there will be drastically more finite startpoints than endpoints, with the far majority of homotopy paths tracking toward roots at infinity.

FRG solves this problem by constructing start systems with the exact monomial structure as the target system.
This is accomplished by generating a random linkage and extracting a start system from its motion and a startpoint from its dimensions.
This single startpoint will indeed track to a finite root of the target system.
To get a second root, this process is repeated.
As the set of finite target roots we aim to obtain is very large, chances are that this second startpoint will track to a different endpoint, with no guarantee.
Repeating this process, roots are accumulated.
As FRG trials progress, eventually the odds of acquiring a new root become unfavorable.
More and more duplicate roots are computed.
FRG trades away infinite root computations for duplicate root computations.  
For sparse systems, the latter tends to be far fewer than the former, making it a good trade-off.
The frequency of duplicate roots was characterized in \cite{plecnikStudyFindingFinite2017}.
Tracking their occurrence allows an in-process estimate of the percentage of the total root set that has been obtained.

FRG provides additional computation savings by exploiting known solution structures in a straightforward way.
For linkage synthesis equations, this structure is primarily provided by the presence of linkage cognates.
The cognate of a single degree-of-freedom linkage is another linkage with different dimensions that exactly reproduces some aspect of the original linkage's continuous motion.
For a given linkage type (e.g. Stephenson II) and motion of interest (e.g. timed curve generation), the presence and number of cognates is often known.
As well, geometric transformations between cognates are known too.
Using these transformations, an entire set of cognate roots can be quickly computed from one endpoint.
Each root in a cognate set is a separate isolated solution, and cognate sets have no intersection with each other.
Combining cognate structures with other existing symmetries (if present) partitions target roots into a smaller number of sets, thereby reducing the expected computational load by the multiple of the size of a single solution set.

@@

Although physically relevant values were not used, the rest of the variables and parameters within $\mathbf{z}$ and $\mathbf{q}$ are computed from the forward kinematics equations of a physical six-bar model.
Physical or not, the result still satisfies Eqn. (\ref{system}), which is our goal at the moment.
These forward kinematics equations are included in Appendix \ref{app:fwd_kin}.
As a six-bar is a one degree-of-freedom linkage, in order to extract random configurations from its motion, we must provide random values for a single configuration parameter.
We choose $R_j\*U_j$, $j=1,\ldots,7$, the complex number associated with angle $\rho_j-\mu_j$, because it makes the forward kinematics computations simple and fast.
It may be noted that the complexity of the solution process of the forward kinematics is dependent on the choice of a specified configuration parameter.
Perhaps intuitively, $R\*U$ is a good choice because it defines one angle of the floating four-bar $DGHF$, which segments calculations to one variable at a time after that.
Solving the forward kinematics equations provides all remaining values in $\mathbf{z}$ and $\mathbf{q}$.
A homotopy path may then be tracked from the startpoint $\mathbf{z}$ that solves the system defined by $\mathbf{q}$ to a finite root that solves a target system defined by a different set of parameters.

@@

Using the start system construction method of Section \ref{sec:start_sys} and exploiting the cognate structure of Section \ref{sec:cognates}, FRG was applied to find the ab initio roots $\mathbf{z}$ of a numerically general target system $\mathcal{S}(\mathbf{z},\mathbf{q}_1)=0$.
Target parameters $\mathbf{q}_1$ were randomly generated and are printed in Appendix \ref{app:fpm}.
After generating this ab initio solution, these roots can be used repeatedly in conjunction  with the parameter homotopy method to solve for any other system $\mathcal{S}(\mathbf{z},\mathbf{q}_2)=0$, where $\mathbf{q}_2$ might be defined by a specific synthesis task.
In Section \ref{sec:leg_app}, we will define $\mathbf{q}_2$ according to analyses in Section \ref{sec:dynamic_mock-up}, to design a novel machine.

@@

\begin{figure}[!b]
\centering
\includegraphics[scale=0.6]{frg_results}
\caption{The accumulation of roots over the procession of the FRG algorithgm.  An estimated 99.0\% of roots were found in $3.56 \times 10^6$ trials.  To find 99.9\% would take about 50\% more computational effort.}
\label{frg_results}
\end{figure}

@@

The cycling foot path is broken into three regions.  
First, the foot point makes ground contact and mechanical advantage decreases, nearly stalling motion and energizing the series-elastic element.
Second, while still in stance mechanical advantage increases, converting elastic energy into high-powered propulsion.
And third, the foot goes out of contact and recycles back to its starting position.
Although only a single low mechanical advantage region was desired, a second is seen in the unloaded regions of Fig. \ref{synth_results}.
It was common to nearly all designs that had the foot path entirely below the ground pivots, that installing a low mechanical advantage region on one part of the curve begot another low mechanical advantage region elsewhere.
It is unclear whether it is possible to exclude this second region and maintain pivots above the foot path.
This just might be the circumstance of the design space we are navigating.
As the second low spot appears in the unloaded region, it is not problematic.

@@

Fourier coefficients for the path displayed in Fig.~\ref{clickspec_path}.
